### 2023-08-28 paper/FPF-WG1.tex
small typo
new nnpdf40 plots
paper abstract

Proton-proton collisions at the LHC produce an intense collimated beam of high-energy (TeV) neutrinos
in the forward direction.
%
The recent  observation of LHC neutrinos by the FASER$\nu$ and SND@LHC experiments
indicates that this hitherto ignored beam becomes available for scientific investigations.
%
Neutrino deep-inelastic scattering (DIS) is known
to provide a sensitive probe of the quark flavour separation in nucleons
and nuclei.
%
Here we quantify the projected impact of DIS neutrino structure functions at the LHC
on the parton distribution functions (PDFs) of protons and heavy nuclei.
%
We generate differential structure function DIS pseudo-data 
for  FASER$\nu$ and SND@LHC based on the Run III luminosity,
as well as for the FASER$\nu$2, AdvSND, and FLArE experiments
to be  hosted at the proposed
 Forward Physics Facility (FPF) operating concurrently with the High Luminosity LHC.
 %
 By using both the Hessian profiling of PDF4LHC21 with {\sc\small xFitter} and
 the  NNPDF open-source framework,
 we highlight the impact on the proton and nuclear PDFs of the FPF
 experiments in a kinematic region in $x$ and $Q^2$ which is comparable to that
 to be covered at the upcoming
 Electron-Ion Collider (EIC).
 %
 This sensitivity is found to be the largest for  strangeness as well as for
 the up and down valence quark PDFs.
%
 Our analysis demonstrates how exploiting the potential
 of this unique LHC neutrino beam  effectively
extends the CERN infrastructure with a ``Neutrino-Ion Collider''.

@@

% REsults for the proton PDFs, using NNPDF and PDF4LHC21/xfitter
\input{sec-protonPDFs}

>>>>

Proton-proton collisions at the LHC produce an intense collimated beam of high-energy (TeV) neutrinos
in the forward direction.
%
The recent  observation of LHC neutrinos by the FASER$\nu$ and SND@LHC experiments
indicates that this hitherto ignored beam becomes available for scientific investigations.
%
Neutrino deep-inelastic scattering (DIS) is known
to provide a sensitive probe of the quark flavour separation in nucleons
and nuclei.
%
Here we quantify the projected impact of DIS neutrino structure functions at the LHC
on the parton distribution functions (PDFs) of protons and heavy nuclei.
%
We generate differential structure function DIS pseudo-data 
for  FASER$\nu$ and SND@LHC based on the Run III luminosity,
as well as for the FASER$\nu$2, AdvSND, and FLArE experiments
to be  hosted at the proposed
 Forward Physics Facility (FPF) operating concurrently with the High Luminosity LHC.
 %
 By using both the Hessian profiling of PDF4LHC21 with {\sc\small xFitter} and
 the  NNPDF open-source framework,
 we highlight the impact on the proton and nuclear PDFs of the FPF
 experiments in a kinematic region in $x$ and $Q^2$ comparable to that
 covered by the upcoming
 Electron-Ion Collider (EIC).
 %
 This sensitivity is found to be the largest for  strangeness as well as for
 the up and down valence quark PDFs, and lead to improved theoretical
 predictions for key scattering processes at the HL-LHC.
%
 Our analysis demonstrates how exploiting the potential
 of this unique LHC neutrino beam  effectively
extends the CERN infrastructure with a ``Neutrino-Ion Collider''.

@@

% REsults 
\input{sec-results}

% Pheno
\input{sec-pheno}
